NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-08-16 paper/Chapters/Chapter4.tex
discussion updated

\section{Main Findings}

\subsection{Carbohydrate eating patterns}

@@

\subsection{Association between carbohydrate eating patterns and health outcomes}

@@

\begin{itemize}
	\item MLCA ignored the order of observation days.
	\item We used the maximum probability rule and ignored that these are just probabilities.
\end{itemize}

@@

>>>>

%\section{Main Findings}

\section{Carbohydrate eating patterns}

@@

\section{Association between carbohydrate eating patterns and health outcomes}

Among men, who were classified as moderate carbohydrate eaters probably had lower odds of having hypertension, after adjustment of age, live with partner or not, educational level, BMI, smoking status and total energy intake. As discussed above, moderate carbohydrate eaters turned to have meals (or energy consumption) later in time compared with high carbohydrate eaters, but low carbohydrate eaters also consumed large amount of energy (from both fat and alcohol) at night. Therefore, considering that moderate carbohydrate eaters were younger than low carbohydrate eaters (although age was adjusted in the full models), there is probably reverse causality exists here (also due to the nature of cross-sectional study). That is, they were potentially both late eaters, however, with their age increased (and so as increased health-related problems/concern) some of them modified their habits, such as quit smoking, replace carbohydrate food with other energy sources which lead to the phenomenon of lower odds of hypertension in moderate carbohydrate eaters. Although the hypothesis cannot be determined by NDNS RP's cross-sectional data, if these theories were true, the energy sources they used to replace carbohydrate in their diet were apparently not very wisely chosen.

Among women, whether living with a partner became an interaction factor for the associations between carbohydrate eating patterns and BMI and abdominal obesity (WC). Directions of the associations were opposite to each other depending on whether women were living with a partner or not. This interaction effect was more obvious when looking at abdominal obesity measurement. High carbohydrate eaters had lower BMI and WC in those lived with their partner, while moderate carbohydrate eaters had higher WC in those who lived alone after adjustment of age, education level, smoking status, total energy intake, and alcohol consumption. High carbohydrate eaters who were characterised with high and early in the day energy consumption and low fat and alcohol intake may reflect a healthier diet and lifestyle, but this might be different between women who lived alone and those who lived with their partners. It was often assumed that live alone may associated with lower diversity of food intake, and a higher likelihood of having an unhealthy dietary pattern \parencite{hanna2015relationship}. Therefore, there may be differences in the actual contents consumed in the high carbohydrates eaters, or there may be other social, psychological or lifestyle related factors related with living alone which we did not included in the models, so that the inverse association between high carbohydrate eating pattern and BMI or abdominal obesity were only observed among women who lived with partners, further analysis is needed. Whereas the reason why moderate carbohydrate eaters' WC was larger than low carbohydrate eaters only among women who lived alone is unknown, given that the evidence of this association was weak and borderline significant, whether it was just a false positive result should be explored in other studies.

%but if the reverse causality reason still applies, women who lived alone may be less likely to modify their diet (replacing carbohydrate with fat or alcohol) and therefore they stayed

%Women lived with partners had higher proportion of being classified as high carbohydrate eaters

@@

\begin{itemize}
	\item MLCA ignored the order of observation days.
	\item We used the maximum probability rule and ignored that these are just probabilities. but inclusive MLCA might perform better.
	\item we do not have the information of whether the participants were doing job that requires shift work.
	\item dietary report under estimation
	\item findings may not be generalizable to populations from other countries.
\end{itemize}

@@

We have successfully defined carbohydrate eating patterns in the general population in the UK adults using the NDNS RP database in both observation day level and participant level. Low carbohydrate eaters turned to have more energy that contributed by both fat and alcohol. Moderate carbohydrate eaters consumed the lowest total energy, while they had the tendency of having meals later in time-of-day. High carbohydrate eaters consumed most of their carbohydrate as well as energy earlier in time-of-day. These dietary patterns specifically for carbohydrate intake were found to be differed by timing, quantity and resources of energy consumption. Compared with low carbohydrate eaters, men had moderate carbohydrate eating pattern may associated with a lower prevalence of hypertension, women in this latent class who lived alone may associated with a larger waist circumferences. Among women who lived with partners, high carbohydrate eating pattern was associated with both lower BMI and smaller waist circumferences. Future studies exploring how such carbohydrate eating patterns may relate longitudinally to change of obesity, hypertension and diabetes incidence and other health outcomes are needed.

### 2018-08-16 paper/main.tex
discussion updated

\thesistitle{The time patterns of carbohydrate intake in the UK adults -- the National Diet and Nutrition Survey 2008/09-15/16 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Professor Luigi \textsc{Palla}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{MSc in Medical Statistics} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Chaochen \textsc{Wang}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

@@

\textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
\textbf{A1c} & Haemoglobin \textbf{A1c}: Glycated hemoglobin \\
%\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
\textbf{BMI} & \textbf{B}ody \textbf{M}ass \textbf{I}ndex \\
%\textbf{cAIC} & \textbf{c}onsistent \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
\textbf{BIC} & \textbf{B}ayesian \textbf{I}information \textbf{C}riterion \\
\textbf{CI}  & \textbf{C}onfidence \textbf{I}nterval \\
\textbf{DM}  & \textbf{D}iabetes \textbf{M}ellitus \\
\textbf{EM}  & \textbf{E}xpectation \textbf{M}aximazation  \\
\textbf{FSA} & \textbf{F}ood \textbf{S}tandards \textbf{A}gency  \\
\textbf{HDL} & \textbf{H}igh \textbf{D}ensity \textbf{L}ipoprotein cholesterol \\
\textbf{LDL} & \textbf{L}ow \textbf{D}ensity \textbf{L}ipoprotein cholesterol \\
\textbf{LCA} & \textbf{L}atent \textbf{C}lass \textbf{A}nalysis\\
%\textbf{LCGA} & \textbf{L}atent \textbf{C}lass \textbf{G}rowth \textbf{A}nalysis \\
%\textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
\textbf{MAFF} & \textbf{M}inistry of \textbf{A}griculture, \textbf{F}isheries and \textbf{F}ood \\
%\textbf{MAR} & \textbf{M}issing \textbf{A}t \textbf{R}andom \\
%\textbf{MCAR} & \textbf{M}issing \textbf{C}ompletely \textbf{A}t \textbf{R}andom \\
\textbf{MLCA} & \textbf{M}ultilevel \textbf{L}atent \textbf{C}lass \textbf{A}nalysis \\
%\textbf{MNAR} & \textbf{M}issing \textbf{N}ot \textbf{A}t \textbf{R}andom \\
\textbf{ML} & \textbf{M}aximum \textbf{L}ikelihood \\
\textbf{NDNS} & the \textbf{N}ational \textbf{D}iet and \textbf{N}utrition \textbf{S}urvey \\
\textbf{OR} & \textbf{O}dds \textbf{R}atio \\
\textbf{PHE} & \textbf{P}ublic \textbf{H}ealth \textbf{E}ngland  \\
\textbf{PSUs} & \textbf{P}rimary \textbf{S}ampling \textbf{U}nits \\
\textbf{TC} & \textbf{T}otal \textbf{C}holesterol \\
\textbf{TG} & \textbf{T}ri\textbf{g}lycerides \\
\textbf{WC}   & \textbf{W}aist \textbf{C}ircumference \\
\end{abbreviations}

>>>>

\thesistitle{The time and quantity patterns of carbohydrate intake in the UK adults -- the National Diet and Nutrition Survey 2008/09-15/16 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Professor Luigi \textsc{Palla}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{MSc in Medical Statistics} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Chaochen \textsc{Wang}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

@@

\textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
\textbf{A1c} & Haemoglobin \textbf{A1c}: Glycated hemoglobin \\
%\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
\textbf{BMI} & \textbf{B}ody \textbf{M}ass \textbf{I}ndex \\
%\textbf{cAIC} & \textbf{c}onsistent \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
\textbf{BIC} & \textbf{B}ayesian \textbf{I}information \textbf{C}riterion \\
\textbf{CI}  & \textbf{C}onfidence \textbf{I}nterval \\
\textbf{DM}  & \textbf{D}iabetes \textbf{M}ellitus \\
%\textbf{EM}  & \textbf{E}xpectation \textbf{M}aximazation  \\
\textbf{FSA} & \textbf{F}ood \textbf{S}tandards \textbf{A}gency  \\
\textbf{HDL} & \textbf{H}igh \textbf{D}ensity \textbf{L}ipoprotein cholesterol \\
\textbf{LDL} & \textbf{L}ow \textbf{D}ensity \textbf{L}ipoprotein cholesterol \\
\textbf{LCA} & \textbf{L}atent \textbf{C}lass \textbf{A}nalysis\\
%\textbf{LCGA} & \textbf{L}atent \textbf{C}lass \textbf{G}rowth \textbf{A}nalysis \\
%\textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
\textbf{MAFF} & \textbf{M}inistry of \textbf{A}griculture, \textbf{F}isheries and \textbf{F}ood \\
%\textbf{MAR} & \textbf{M}issing \textbf{A}t \textbf{R}andom \\
%\textbf{MCAR} & \textbf{M}issing \textbf{C}ompletely \textbf{A}t \textbf{R}andom \\
\textbf{MLCA} & \textbf{M}ultilevel \textbf{L}atent \textbf{C}lass \textbf{A}nalysis \\
%\textbf{MNAR} & \textbf{M}issing \textbf{N}ot \textbf{A}t \textbf{R}andom \\
\textbf{ML} & \textbf{M}aximum \textbf{L}ikelihood \\
\textbf{NDNS} & the \textbf{N}ational \textbf{D}iet and \textbf{N}utrition \textbf{S}urvey \\
\textbf{OR} & \textbf{O}dds \textbf{R}atio \\
\textbf{PHE} & \textbf{P}ublic \textbf{H}ealth \textbf{E}ngland  \\
\textbf{PSUs} & \textbf{P}rimary \textbf{S}ampling \textbf{U}nits \\
\textbf{TC} & \textbf{T}otal \textbf{C}holesterol \\
\textbf{TG} & \textbf{T}ri\textbf{g}lycerides \\
\textbf{WC}   & \textbf{W}aist \textbf{C}ircumference \\
\end{abbreviations}
